Universal Anonymous Signatures

### 2022-07-28 prism-backend/research/gsac/formal-uas.tex
Migrated syntax, model and construction where issuers=users. RS construction fixed.

@@

\begin{description}
\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all the other functions, even if not explicitly listed in their
  input parameters.
\item[$\IKeyGen(\parm,\fissue) \rightarrow (\ipk,\isk)$.] Given \parm, and the
  function \fissue for checking that credential requestors meet the conditions
  to be issued a credential, an issuer runs \IKeyGen to generate its issuing key
  pair. 
\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given \parm, and the
  function \finsp, an opener runs \OKeyGen to generate its opening key pair.
  The function \finsp defines the type of utility that will be extractable from
  signatures.
\item[$\UKeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, returns a user's
  key pair.
\item[$\langle
  \Obtain(\usk,\cidu,\ipk,\sCred,\attrs),
  \Issue(\isk,\cidi,\sipk,\attrs))  
  \rangle \rightarrow \langle \Cred/\bot,R/\bot
  \rangle$.] %
  This interactive protocol lets a user with key \usk running the \Obtain
  process, receive a credential $\Cred=(\cid,\attrs,\cred,\ipk)$
  from an issuer in the system. $\cid=(\cidi,\cidu)$ is a unique identifier for
  the credential, where issuer and user randomly pick \cidi and \cidu,
  respectively (to ease notation, whenever we write just \cid, we mean $(\cidi,
  \cidu)$). \ipk is the issuer's public key and \cred is the actual credential,
  on attribute set \attrs. The user may leverage a set of previously obtained
  credentials $\sCred=\lbrace (\cid_i=(\cidi_i,\cidu_i),\cattrs_i,\cred_i,
  \ipk_i)\rbrace_{i\in[n]}$, from which we may omit the $\ipk_i$s for
  readability. The user outputs the produced credential \Cred, while the issuer
  outputs $R \gets (\yissue,\utrans)$, for some value $\yissue$ output by
  the \fissue defined by the issuer, and $\utrans$ being the transcript of
  the communication.
\item[$\Sign(\usk,\opk,\sCred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
  Upon receiving a user secret key \usk, opener public key \opk, a set of
  credentials \sCred, a message \msg and evaluation function \feval, returns
  signature \sig, and a plaintext value \yeval. We use use \Sig to denote the
  tuple $(\sig,\yeval)$.
\item[$\Verify(\opk,\sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
  Checks whether $\Sig = (\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys in \sipk, for evaluation function \feval and opener key \opk.
\item[$\Open(\osk,\sipk,\Sig,\msg,\feval) \rightarrow
  (\yinsp,\iproof)/\bot$.]
  Executed by the opener with private key \osk. Receives a signature $\Sig=
  (\sig,\yeval)$ over message \msg and evaluation function \feval,
  generated using credentials issued by the issuers with public keys in \sipk.
  If \Sig is valid, the function outputs a value $\yinsp$, and a proof of
  correct opening \iproof.
\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval)$
  over message \msg, and for evaluation function \feval. 
\end{description}

@@

\paragraph{Global Variables.} %
Users are referred to with user identifiers, \uid; for credentials, we use \cid;
for issuers, \iid; and for openers, \oid.  In all cases, we use bold font to
denote sets: e.g., \scid and \siid denote sets of credential and issuer
identifiers. All tables/sets are initialized as empty tables/sets. For
notational convenience, we often use these identifiers instead of the
corresponding user/issuer/opener keys.

@@

\begin{description}
\item[\IGEN.] Adds a new issuer to the game, generating its keypair and setting
  the associated issuance function.
\item[\OGEN.] Adds a new opener to the game, generating its key pair and
  setting the associated evaluation and inspection functions.
\item[\ICORR.] Corrupts an existing (and honest) issuer, by giving its secret
  key to the adversary.
\item[\OCORR.] Corrupts an existing (and honest) opener, by giving its secret
  key to the adversary.  
\item[\HUGEN.] Adds a new honest user to the game, by honestly generating
  the user's key pair.
\item[\CUGEN.] Adds a new corrupt user to the game or, if the specified
  user already exists and is honest, corrupts it, leaking its key and
  credentials.
\item[\RREG.] Reads the given transcript table entry.
\item[\WREG.] Sets a transcript table entry to the given value.
\item[\OBTISS.] Lets the adversary add a new honestly generated credential to
  the game, on behalf of an honest user.
\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer, by
  letting it interact with honest users who want to receive credentials.
\item[\ISSUE.] Allows the adversary to play the role of dishonest users,
  requesting an honest issuer to produce credentials for them.
\item[\SIGN.] Lets the adversary get signatures from credentials belonging
  to honest users.
\item[\OPEN.] Given an honestly produced signature, outputs the result of the
  opening function, along with a correctness proof.
\item[\OBTCHALb.] Upon receiving a target credential identifier, two challenge
  users and credential sets, an honest issuer identifier, and a set of
  attributes, issues a credential for the challenge user and credential set
  defined by the bit $b$. 
\item[\CHALb.] Upon receiving two challenge users and credential sets, a common
  singing evaluation function and a message, returns a signature produced by one
  of these two user and credential sets, defined by the bit $b$.
\end{description}

@@

        \procedure{$\IGEN(\iid,\fissue)$}{%
          \pcif \iid \in \HI \lor \iid \in \CI: \pcreturn \bot \\
          \pcif \fissue \notin \famfissue: \pcreturn \bot \\
          (\ipk,\isk) \gets \IKeyGen(\parm) \\
          \IK[\iid] \gets ((\ipk,\fissue),\isk) \\
          \HI \gets \HI \cup \lbrace \iid \rbrace \\
          \pcreturn \ipk \\
        }

        \procedure{$\ICORR(\iid)$}{%
          \pcif \iid \in \CI \lor \iid \notin \HI: \pcreturn \bot \\
          \HI \gets \HI \setminus \lbrace \iid \rbrace \\
          \CI \gets \CI \cup \lbrace \iid \rbrace \\
          \pcreturn \isk \\
        }

        \procedure{$\HUGEN(\uid)$}{%
          \pcif \uid \in \HU \lor \uid \in \CU: \pcreturn \bot \\
          (\upk,\usk) \gets \UKeyGen(\parm) \\
          \UK[\uid] \gets (\upk,\usk);
          \HU \gets \HU \cup \lbrace  \uid \rbrace \\
          \pcreturn \top \\
        }

        \procedure{$\RREG(i)$}{%
          \pcreturn \trans[i]
        }

@@

        \procedure{$\OGEN(\oid,\finsp)$}{%
          \pcif \oid \in \HO \lor \oid \in \CO: \pcreturn \bot \\
          \pcif \finsp \notin \famfinsp: \pcreturn \bot \\
          (\opk,\osk) \gets \OKeyGen(\parm) \\
          \OK[\oid] \gets ((\opk,\finsp),\osk) \\
          \HO \gets \HO \cup \lbrace \oid \rbrace \\
          \pcreturn \opk \\
        }

@@

        \procedure{$\CUGEN(\uid)$}{%          
          \pcif \uid \in \CU: \pcreturn \bot \\
          \CU \gets \CU \cup \lbrace \uid \rbrace \\          
          \pcif \uid \in \HU: \\
          \pcind \HU \gets \HU \setminus \lbrace \uid \rbrace; \\
          \pcind \pcreturn (\UK[\uid],\CRED[\uid]) \\
          \pcelse: \UK[\uid] = \bot \\          
          \pcreturn \top \\
        }

@@

\begin{description}
\item[$\SimSetup(1^\secpar) \rightarrow (\parm,\trap)$.] Given a security
  parameter, outputs global (simulated) parameters \parm whose distribution is
  indistinguishable to that produced by the \Setup algorithm, as well as a
  trapdoor \trap.
\item[$\ExtractIssue(\trap,\utrans) \rightarrow ((\upk,\usk),\sCred=
  \lbrace(\cid_i,\attrs_i,\cred_i) \rbrace_{i \in [n]})$.]
  Receives trapdoor \trap and an $\langle \Obtain, \Issue \rangle$ transcript,
  and returns the credential set \sCred, if any, involved in the request. It
  needs an honest issuer as, otherwise, the transcripts won't be available. 
\item[$\ExtractSign(\trap,\oid,\lbrace \iid_i \rbrace_{i \in [n]},\Sig,\msg,
  \feval) \rightarrow ((\upk,\usk),\sCred=\lbrace(\cid_i,\attrs_i,\cred_i)
  \rbrace_{i \in [n]},\yeval^1,\yinsp)$.] Receives a trapdoor \trap, a signature
  \Sig, as well as the opener identifier \oid, and the identifiers of all
  issuers of the credentials used to produce the signature over \msg, and for
  \feval. It outputs the user secret key and credential set \sCred used to
  generate the signature, and the $\yeval^1$ and \yinsp values.
% \item[$\IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk)$.] Returns $1$ if
%   \cred has been issued over attributes $\attrs_{\cred}$ and for a user with
%   secret key \usk, by honest issuer with public key \ipk. Otherwise, it returns
%   $0$.

@@

\begin{figure}[htp!]
  \centering
  \scalebox{0.9}{
    \procedure[linenumbering]{$\ExpCorrect(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\uid,\oid,\scid,\msg,\feval)
      \gets \adv^{\IGEN,\OGEN,\HUGEN,\OBTISS,\RREG}(\parm) \\
      \pcif \feval \notin \famfeval: \pcreturn 0 \\
      \pcif \OWNR[\scid] \neq \uid: \pcreturn 0 \\
      (\Sig = (\sig,\yeval)) \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\scid,\msg,
      \feval) \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) = 0: \pcreturn 1 \\
      \pcfor \cid \in \scid \pcdo: \\
      \pcind \textrm{Parse}~\CRED[\cid]~\textrm{as}~
      (\cdot,\cdot,\cdot,\attrs,n,\lbrace(\cid_i,\cdot)\rbrace_{i\in[n]})) \\
%      \pcind \textrm{Let}~\scid^{\cid}~\textrm{be the {\cid}s used to obtain}
%      ~\cid;~\textrm{Parse}~\PUBIK[\ISR[\cid]]~\textrm{as}~((\cdot,
%      \fissue^{\cid}),\cdot)\\
      \pcind \textrm{Parse}~\trans[\cid]~\textrm{as}~(\yissue,\utrans);
      \PUBIK[\cid]~\textrm{as}~((\cdot,\fissue),\cdot)\\
      \pcind \pcif \fissue(\PUBUK[\uid],\attrs,
      (\lbrace(\cid_i,\ATTR[\cid_i])\rbrace_{i\in[n]})) \neq \yissue:
      \pcreturn 1 \\
      (\yeval^0,\yeval^1) \gets \feval(\PUBUK[\uid],(\scid,\ATTR[\scid]),\msg) \\
      \pcif \yeval^0 \neq \yeval: \pcreturn 1 \\
      (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\scid],\yinsp,\iproof,\Sig,\msg,\feval)
      = 0~\lor \\
      \pcind \yinsp \neq \finsp^\oid((\yeval,\yeval^1),
      \PUBUK[\uid],(\scid,\ATTR[\scid]),\msg)): \\
      \pcind \pcreturn 1 \\
      \pcreturn 0
    }
  }
  \caption{Correctness experiment for \UAS schemes.}
  \label{fig:exp-uas-corr}
\end{figure}

@@

The formal specification of the anonymity games is given in
\figref{fig:exp-uas-anonb}, where
$\OIssAnon \gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,
\OO\rbrace\CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\OBTCHALb)$, and $\OSigAnon
\gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace
\CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\CHALb)$.

@@

For both \ExpForgeIssue and \ExpForgeSign (in \figref{fig:exp-uas-unfor}), the
adversary is given access to the oracle set $\Oforgeissue = \Oforgesign \gets
\lbrace\HU,\CU\rbrace\GEN,\IGEN,\OGEN,\OCORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN$.

\begin{figure}[htp!]
  \centering
  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        \cid \gets \adv^{\Oforgeissue}(\parm) \\
        \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot:
        \pcreturn 0 \\
        \textrm{Parse}~\trans[\cid]~\textrm{as}~(\yissue,\utrans) \\
        % (\usk,\sCred) \gets \ExtractIssue(\trap,\trans[\cid]) \\
        ((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]})
        \gets \ExtractIssue(\trap,\utrans) \\
        % \pcfor i \in [n]: (\usk_i,\cdot) \gets \ExtractIssue(\trap,
        % \trans[\cid_i]) \\
        % \pcif \exists i \in [n]~\suchthat~\usk \neq \usk_i: \pcreturn 1 \\
        \pcif \fissue(\upk,\ATTR[\cid],\lbrace (\cid_i,\attrs_i)
        \rbrace_{i\in[n]}) = \yissue:
        \pcreturn 1 \\
        \pcif \OWNR[\cid] \notin \HU \cup \CU: \pcreturn 1 \\
        \pcreturn 0
      }
      \vspace*{0.5em}

@@

In the non-frameability definition for \UAS, given in experiment \ExpNonframe in
\figref{fig:exp-uas-frame}, the adversary is challenged to produce a signature
and opening proof that is accepted by \Verify and \Judge, respectively. From
the signature, we then extract the secret data used to generate it. The
adversary wins if the signature and opening proof are accepted, but the \yeval
or \yinsp values do not match what they should be based on the extracted data;
or if the signature can be associated to the secret key of an honest user who
did not produce it (i.e., no matching call to \SIGN exists). In the game, the
adversary has access to the oracles in $\Oframe \gets
\lbrace\HU,\CU\rbrace\GEN, \lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,
\WREG,\OBTAIN,\SIGN$.

@@

From them, we build \CUASGen as follows.

@@

\paragraph{$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.} %
Each issuer first parses \parm as $(\cdot,\SBCMparm,
\Sparm,\cdot,\cdot,\cdot,\cdot,\cdot)$. Then, runs $(\Svk,\Ssk) \gets
\SKeyGen(\Sparm)$, $(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$,
$\sig_{\fissue} \gets \SSign(\Ssk,\fissue)$, $\ipk \gets (\SBCMparm,\Svk,
\fissue,\sig_{\fissue})$, $\isk \gets \Ssk$ and return $(\ipk,\isk)$.

>>>>

\todo{Clarify that, for us, issuers and users are essentially the same thing.}

@@

\begin{description}
\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all the other functions, even if not explicitly listed in their
  input parameters.
\item[$\KeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, a user runs
  \KeyGen to generate its user key pair. 
\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given \parm, and the
  function \finsp, an opener runs \OKeyGen to generate its opening key pair.
  The function \finsp defines the type of utility that will be extractable from
  signatures.
\item[$\ISet((\upk,\usk),\fissue) \rightarrow \ipk$.] Given a user key
  pair, and an issuance function \fissue for checking that credential requestors
  meet some conditions to be issued a credential, an existing user runs \ISet to
  extend the user public key, enabling this user to issue credentials meeting
  \fissue.
%\item[$\UKeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, returns a user's
%  key pair.
\item[$\langle
  \Obtain(\usk,\cidu,\ipk,\sCred,\attrs),
  \Issue(\isk,\cidi,\sipk,\attrs))  
  \rangle \rightarrow \langle \Cred/\bot,R/\bot
  \rangle$.] %
  This interactive protocol lets a user with key \usk running the \Obtain
  process, receive a credential $\Cred=(\cid,\attrs,\cred,\ipk)$
  from an issuer in the system. $\cid=(\cidi,\cidu)$ is a unique identifier for
  the credential, where issuer and user randomly pick \cidi and \cidu,
  respectively (to ease notation, whenever we write just \cid, we mean $(\cidi,
  \cidu)$). \ipk is the issuer's public key and \cred is the actual credential,
  on attribute set \attrs. The user may leverage a set of previously obtained
  credentials $\sCred=\lbrace (\cid_i=(\cidi_i,\cidu_i),\cattrs_i,\cred_i,
  \ipk_i)\rbrace_{i\in[n]}$, from which we may omit the $\ipk_i$s for
  readability. The user outputs the produced credential \Cred, while the issuer
  outputs $R \gets (\yissue,\utrans)$, for some value $\yissue$ output by
  the \fissue defined by the issuer, and $\utrans$ being the transcript of
  the communication.
\item[$\Sign(\usk,\opk,\sCred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
  Upon receiving a user secret key \usk, opener public key \opk, a set of
  credentials \sCred, a message \msg and evaluation function \feval, returns
  signature \sig, and a plaintext value \yeval. We use use \Sig to denote the
  tuple $(\sig,\yeval)$.
\item[$\Verify(\opk,\sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
  Checks whether $\Sig = (\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys in \sipk, for evaluation function \feval and opener key \opk.
\item[$\Open(\osk,\sipk,\Sig,\msg,\feval) \rightarrow
  (\yinsp,\iproof)/\bot$.]
  Executed by the opener with private key \osk. Receives a signature $\Sig=
  (\sig,\yeval)$ over message \msg and evaluation function \feval,
  generated using credentials issued by the issuers with public keys in \sipk.
  If \Sig is valid, the function outputs a value $\yinsp$, and a proof of
  correct opening \iproof.
\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval)$
  over message \msg, and for evaluation function \feval. 
\end{description}

@@

\paragraph{Global Variables.} %
\todo{Clarify that {\iid}s are just {\uid}s.}
Users are referred to with user identifiers, \uid; for credentials, we use \cid;
for issuers, \iid; and for openers, \oid.  In all cases, we use bold font to
denote sets: e.g., \scid and \siid denote sets of credential and issuer
identifiers. All tables/sets are initialized as empty tables/sets. For
notational convenience, we often use these identifiers instead of the
corresponding user/issuer/opener keys.

@@

\begin{description}
% \item[\IGEN.] Adds a new issuer to the game, generating its keypair and setting
%   the associated issuance function.
\item[\UGEN.] Adds a new user to the game, generating its keypair.  
\item[\OGEN.] Adds a new opener to the game, generating its key pair and
  setting the associated evaluation and inspection functions.
% \item[\ICORR.] Corrupts an existing (and honest) issuer, by giving its secret
%   key to the adversary.
\item[\ISET.] ``Upgrades'' an user to become an issuer, specifying its
  associated issuance function.
\item[\UCORR.] Corrupts an existing (and honest) user, by giving its secret
  key to the adversary. If the user was also an issuer, it becomes a corrupt
  issuer too.
\item[\OCORR.] Corrupts an existing (and honest) opener, by giving its secret
  key to the adversary.
% \item[\HUGEN.] Adds a new honest user to the game, by honestly generating
%   the user's key pair.
% \item[\CUGEN.] Adds a new corrupt user to the game or, if the specified
%   user already exists and is honest, corrupts it, leaking its key and
%   credentials.
\item[\RREG.] Reads the given transcript table entry.
\item[\WREG.] Sets a transcript table entry to the given value.
\item[\OBTISS.] Lets the adversary add a new honestly generated credential to
  the game, on behalf of an honest user.
\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer, by
  letting it interact with honest users who want to receive credentials.
\item[\ISSUE.] Allows the adversary to play the role of dishonest users,
  requesting an honest issuer to produce credentials for them.
\item[\SIGN.] Lets the adversary get signatures from credentials belonging
  to honest users.
\item[\OPEN.] Given an honestly produced signature, outputs the result of the
  opening function, along with a correctness proof.
\item[\OBTCHALb.] Upon receiving a target credential identifier, two challenge
  users and credential sets, an honest issuer identifier, and a set of
  attributes, issues a credential for the challenge user and credential set
  defined by the bit $b$. 
\item[\CHALb.] Upon receiving two challenge users and credential sets, a common
  singing evaluation function and a message, returns a signature produced by one
  of these two user and credential sets, defined by the bit $b$.
\end{description}

@@

        % \procedure{$\IGEN(\iid,\fissue)$}{%
        %   \pcif \iid \in \HI \lor \iid \in \CI: \pcreturn \bot \\
        %   \pcif \fissue \notin \famfissue: \pcreturn \bot \\
        %   (\ipk,\isk) \gets \IKeyGen(\parm) \\
        %   \IK[\iid] \gets ((\ipk,\fissue),\isk) \\
        %   \HI \gets \HI \cup \lbrace \iid \rbrace \\
        %   \pcreturn \ipk \\
        % }

        % \procedure{$\ICORR(\iid)$}{%
        %   \pcif \iid \in \CI \lor \iid \notin \HI: \pcreturn \bot \\
        %   \HI \gets \HI \setminus \lbrace \iid \rbrace \\
        %   \CI \gets \CI \cup \lbrace \iid \rbrace \\
        %   \pcreturn \isk \\
        % }

        % \procedure{$\HUGEN(\uid)$}{%
        %   \pcif \uid \in \HU \lor \uid \in \CU: \pcreturn \bot \\
        %   (\upk,\usk) \gets \UKeyGen(\parm) \\
        %   \UK[\uid] \gets (\upk,\usk);
        %   \HU \gets \HU \cup \lbrace  \uid \rbrace \\
        %   \pcreturn \top \\
        % }

        \procedure{$\UGEN(\uid)$}{%
          \pcif \uid \in \HU \lor \uid \in \CU: \pcreturn \bot \\
          (\upk,\usk) \gets \KeyGen(\parm) \\
          \UK[\uid] \gets (\upk,\usk) \\
          \HU \gets \HU \cup \lbrace \uid \rbrace \\
          \pcreturn \upk \\
        }

        \procedure{$\ISET(\uid,\fissue)$}{%
          \pcif \uid \notin \HU \cup \CU: \pcreturn \bot \\
          \pcif \uid \in \HI \cup \CI: \pcreturn \bot \\
          \pcif \fissue \notin \famfissue: \pcreturn \bot \\
          \ipk \gets \ISet(\UK[\uid],\fissue) \\
          \IK[\uid] \gets ((\ipk,\fissue),\PRVUK[\uid]) \\
          \pcif \uid \in \HU: \HI \gets \HI \cup \lbrace \uid \rbrace \\
          \pcif \uid \in \CU: \CI \gets \CI \cup \lbrace \uid \rbrace \\
          \pcreturn \ipk \\
        }

        \procedure{$\OGEN(\oid,\finsp)$}{%
          \pcif \oid \in \HO \lor \oid \in \CO: \pcreturn \bot \\
          \pcif \finsp \notin \famfinsp: \pcreturn \bot \\
          (\opk,\osk) \gets \OKeyGen(\parm) \\
          \OK[\oid] \gets ((\opk,\finsp),\osk) \\
          \HO \gets \HO \cup \lbrace \oid \rbrace \\
          \pcreturn \opk
        }

@@

        \procedure{$\UCORR(\uid)$}{%
          \pcif \uid \in \CU \lor \uid \notin \HU: \pcreturn \bot \\
          \pcif \uid \in \HI \cup \CI: \pcreturn \bot \\
          \HU \gets \HU \setminus \lbrace \uid \rbrace \\
          \CU \gets \CU \cup \lbrace \uid \rbrace \\
          \pcreturn (\PRVUK[\uid],\CRED[\uid]) \\
        }

        \procedure{$\ICORR(\uid)$}{%
          \pcif \uid \notin \HI: \pcreturn \bot \\
          \HI \gets \HI \setminus \lbrace \uid \rbrace \\
          \CI \gets \CI \cup \lbrace \uid \rbrace \\
          \pcreturn(\PRVUK[\uid],\CRED[\uid]) \\
        }

@@

        % \procedure{$\CUGEN(\uid)$}{%          
        %   \pcif \uid \in \CU: \pcreturn \bot \\
        %   \CU \gets \CU \cup \lbrace \uid \rbrace \\          
        %   \pcif \uid \in \HU: \\
        %   \pcind \HU \gets \HU \setminus \lbrace \uid \rbrace; \\
        %   \pcind \pcreturn (\UK[\uid],\CRED[\uid]) \\
        %   \pcelse: \UK[\uid] = \bot \\          
        %   \pcreturn \top \\
        % }

        \procedure{$\RREG(i)$}{%
          \pcreturn \trans[i] \\
        }

@@

\begin{description}
\item[$\SimSetup(1^\secpar) \rightarrow (\parm,\trap)$.] Given a security
  parameter, outputs global (simulated) parameters \parm whose distribution is
  indistinguishable to that produced by the \Setup algorithm, as well as a
  trapdoor \trap.
\item[$\ExtractIssue(\trap,\utrans) \rightarrow ((\upk,\usk),\sCred=
  \lbrace(\cid_i,\attrs_i,\cred_i) \rbrace_{i \in [n]})$.]
  Receives trapdoor \trap and an $\langle \Obtain, \Issue \rangle$ transcript,
  and returns the credential set \sCred, if any, involved in the request. It
  needs an honest issuer as, otherwise, the transcripts won't be available. 
\item[$\ExtractSign(\trap,\opk,\lbrace \ipk_i \rbrace_{i \in [n]},\Sig,\msg,
  \feval) \rightarrow ((\upk,\usk),\sCred=\lbrace(\cid_i,\attrs_i,\cred_i)
  \rbrace_{i \in [n]},\yeval^1,\yinsp)$.] Receives a trapdoor \trap, a signature
  \Sig, as well as the opener identifier \oid, and the identifiers of all
  issuers of the credentials used to produce the signature over \msg, and for
  \feval. It outputs the user secret key and credential set \sCred used to
  generate the signature, and the $\yeval^1$ and \yinsp values. For notational
  convenience, we overload this function and use \oid and \iid instead of the
  actual opener and issuers' key pairs.
% \item[$\IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk)$.] Returns $1$ if
%   \cred has been issued over attributes $\attrs_{\cred}$ and for a user with
%   secret key \usk, by honest issuer with public key \ipk. Otherwise, it returns
%   $0$.

@@

\begin{figure}[htp!]
  \centering
  \scalebox{0.9}{
    \procedure[linenumbering]{$\ExpCorrect(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\uid,\oid,\scid,\msg,\feval)
      \gets \adv^{\UGEN,\OGEN,\ISET,\OBTISS,\RREG}(\parm) \\
      \pcif \feval \notin \famfeval: \pcreturn 0 \\
      \pcif \OWNR[\scid] \neq \uid: \pcreturn 0 \\
      (\Sig = (\sig,\yeval)) \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\scid,\msg,
      \feval) \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) = 0: \pcreturn 1 \\
      \pcfor \cid \in \scid \pcdo: \\
      \pcind \textrm{Parse}~\CRED[\cid]~\textrm{as}~
      (\cdot,\cdot,\cdot,\attrs,n,\lbrace(\cid_i,\cdot)\rbrace_{i\in[n]})) \\
%      \pcind \textrm{Let}~\scid^{\cid}~\textrm{be the {\cid}s used to obtain}
%      ~\cid;~\textrm{Parse}~\PUBIK[\ISR[\cid]]~\textrm{as}~((\cdot,
%      \fissue^{\cid}),\cdot)\\
      \pcind \textrm{Parse}~\trans[\cid]~\textrm{as}~(\yissue,\utrans);
      \PUBIK[\cid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
      \pcind \pcif \fissue(\PUBUK[\uid],\attrs,
      (\lbrace(\cid_i,\ATTR[\cid_i])\rbrace_{i\in[n]})) \neq \yissue:
      \pcreturn 1 \\
      (\yeval^0,\yeval^1) \gets \feval(\PUBUK[\uid],(\scid,\ATTR[\scid]),\msg) \\
      \pcif \yeval^0 \neq \yeval: \pcreturn 1 \\
      (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\scid],\yinsp,\iproof,\Sig,\msg,\feval)
      = 0~\lor \\
      \pcind \yinsp \neq \finsp^\oid((\yeval,\yeval^1),
      \PUBUK[\uid],(\scid,\ATTR[\scid]),\msg)): \\
      \pcind \pcreturn 1 \\
      \pcreturn 0
    }
  }
  \caption{Correctness experiment for \UAS schemes.}
  \label{fig:exp-uas-corr}
\end{figure}

@@

The formal specification of the anonymity games is given in
\figref{fig:exp-uas-anonb}, where
$\OIssAnon \gets (\lbrace\OO,\UU\rbrace\GEN,\ISET,\ISET,\lbrace\II,
\OO,\UU\rbrace\CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\OBTCHALb)$, and $\OSigAnon
\gets (\lbrace\OO,\UU\rbrace\GEN,\ISET,\ISET,\lbrace\II,\OO,\UU\rbrace
\CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\CHALb)$.

@@

For both \ExpForgeIssue and \ExpForgeSign (in \figref{fig:exp-uas-unfor}), the
adversary is given access to the oracle set $\Oforgeissue = \Oforgesign \gets
\lbrace\OO,\UU\rbrace\GEN,\ISET,\lbrace\OO,\UU\rbrace\CORR,\OBTISS,\ISSUE,\RREG,
\SIGN,\OPEN$.

\begin{figure}[htp!]
  \centering
  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        \cid \gets \adv^{\Oforgeissue}(\parm) \\
        \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot:
        \pcreturn 0 \\
        \textrm{Parse}~\trans[\cid]~\textrm{as}~(\yissue,\utrans);
        \PUBIK[\cid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
        % (\usk,\sCred) \gets \ExtractIssue(\trap,\trans[\cid]) \\
        ((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]})
        \gets \ExtractIssue(\trap,\utrans) \\
        % \pcfor i \in [n]: (\usk_i,\cdot) \gets \ExtractIssue(\trap,
        % \trans[\cid_i]) \\
        % \pcif \exists i \in [n]~\suchthat~\usk \neq \usk_i: \pcreturn 1 \\
        \pcif \fissue(\upk,\ATTR[\cid],\lbrace (\cid_i,\attrs_i)
        \rbrace_{i\in[n]}) = \yissue:
        \pcreturn 1 \\
        \pcif \OWNR[\cid] \notin \HU \cup \CU: \pcreturn 1 \\
        \pcreturn 0
      }
      \vspace*{0.5em}

@@

In the non-frameability definition for \UAS, given in experiment \ExpNonframe in
\figref{fig:exp-uas-frame}, the adversary is challenged to produce a signature
and opening proof that is accepted by \Verify and \Judge, respectively. From
the signature, we then extract the secret data used to generate it. The
adversary wins if the signature and opening proof are accepted, but the \yeval
or \yinsp values do not match what they should be based on the extracted data;
or if the signature can be associated to the secret key of an honest user who
did not produce it (i.e., no matching call to \SIGN exists). In the game, the
adversary has access to the oracles in $\Oframe \gets
\lbrace\OO,\UU\rbrace\GEN,\ISET,\lbrace\II,\OO,\UU\rbrace\CORR,
\WREG,\OBTAIN,\SIGN$.

@@

From them, we build \CUASGen as follows.
\todo{Check if \SSetup etc is still needed...}

@@

% \paragraph{$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.} %
% Each issuer first parses \parm as $(\cdot,\SBCMparm,
% \Sparm,\cdot,\cdot,\cdot,\cdot,\cdot)$. Then, runs $(\Svk,\Ssk) \gets
% \SKeyGen(\Sparm)$, $(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$,
% $\sig_{\fissue} \gets \SSign(\Ssk,\fissue)$, $\ipk \gets (\SBCMparm,\Svk,
% \fissue,\sig_{\fissue})$, $\isk \gets \Ssk$ and return $(\ipk,\isk)$.

\paragraph{$(\upk,\usk) \gets \KeyGen(\parm)$.} %
Each user first parses \parm as $(\cdot,\SBCMparm,
\cdot,\cdot,\cdot,\cdot,\cdot,\cdot)$. Then, runs $(\SBCMvk,\SBCMsk) \gets
\SBCMKeyGen(\SBCMparm)$, $\upk \gets (\parm,\SBCMvk)$, $\usk \gets \SBCMsk$,
and returns $(\upk,\usk)$.
